Predator summary

### 2023-02-09 reports/01_predators.qmd
Change over from SG tto ANT terminology

tar_load(c("predators_agg", "sg_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

## South Georgia winter predators

@@

map_lim <- sf::st_bbox(snpt_sf) %>% 
  sf::st_as_sfc(crs = "EPSG:4326") %>% 
  sf::st_transform(sg_proj()) %>% 
  sf::st_bbox()

ggplot() +
  geom_sf(data = sg_sf) +
  stars::geom_stars(aes(fill = SNPT), data = snpt_stars) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      na.value = NA) +
  expand_limits(fill = 0) +
  coord_sf(xlim = map_lim[c("xmin", "xmax")],
           ylim = map_lim[c("ymin", "ymax")],
           expand = FALSE,
           crs = sg_proj()) +
  theme_minimal() +
  theme(axis.title = element_blank())

>>>>

tar_load(c("predators_agg", "ant_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

## Antarctic Peninsula winter predators

@@

map_lim <- sf::st_bbox(snpt_sf) %>% 
  sf::st_as_sfc(crs = "EPSG:4326") %>% 
  sf::st_transform(ant_proj()) %>% 
  sf::st_bbox()

ggplot() +
  geom_sf(data = ant_sf) +
  stars::geom_stars(aes(fill = SNPT), data = snpt_stars) +
  scale_fill_gradient(low = "lightblue", high = "darkred",
                      na.value = NA) +
  expand_limits(fill = 0) +
  coord_sf(xlim = map_lim[c("xmin", "xmax")],
           ylim = map_lim[c("ymin", "ymax")],
           expand = FALSE,
           crs = ant_proj()) +
  theme_minimal() +
  theme(axis.title = element_blank())
